\sysfull

### 2018-04-15 paper/evaluation.tex
Table 4 revised and ready to be filled in with data

\textcolor{red}{ highlight the difference between Alpaca GCC and Alpaca Clang. Alpaca GCC is about 30\%-40\% faster than Alpaca Clang. Writing Alpaca program by hand is a very trick thing and it is very error prone. Reason: a programmer needs to identify the write-after-read dependencies, change variables' names, and modify instructions accordingly, in general writing Alpaca code by hand is not a recommended, for that a compiler is needed}

@@

@@

We evaluated \sys to show that it is easy to use and efficient across our benchmarks. We evaluate \sys efficiency by comparing its runtime performance to Alpaca. We characterize \sys by studying how its performance varies due to coalescing.

@@

We first need to assess the performance of all coalescing strategies introduced by us in Section~\ref{}.

\textbf{Coalescing Strategies.} Figure~\ref{fig:coalescing} shows the run time of \sys's two coalescing strategies normalized to the run time without
coalescing. We show data from experiments with intermittent power, where intermittency was generated in software
%\todo{Say briefly how we generate full reset with MSP430}{Amjad}
by triggering a reset from software at intervals that were uniformly distributed with an average power availability and unavailability interval of 15\,ms and 10\,ms respectively. Each application ran with the same generated pattern for the fairness of comparison. The results show the benefit from coalescing for most applications, with the
exception of dft, where wasted work dominated the gains from coalescing.
 %\todo{why coalescing for dft does not work but in Fig. 9 does?}{Amjad}
The difference in performance between HC and TSHC strategies is highly
application-dependent, with some applications benefiting from size awareness
while others suffering, due to decisions based on inaccurate prediction of the
actual task energy consumption. The TSHC gains are particularly small (or negative) for applications with narrower range of task sizes in Figure~\ref{fig:task_profiling}.
%\todo{say why this difference is small}{Amjad}.
%For this reason we shall proceed with HD coalescing strategy in subsequent evaluations.

@@

\begin{table}
	\begin{tabular}{| c | c | c | c | c |}
		\hline
		Application & \multicolumn{2}{| c |}{Memory footprint} & No. tasks & SLOC \\
		{} & \sys & Alpaca & {} & {} \\
		\hline\hline
		\textbf{ar} & --- & --- & --- & ---\\
		\hline
	\end{tabular}
		\caption{Comparison between \sys and Alpaca benchmarks.}
		\label{table:compiler_result}\vspace{-0.5cm}
\end{table}

>>>>

\textcolor{red}{highlight the difference between Alpaca GCC and Alpaca Clang. Alpaca GCC is about 30\%-40\% faster than Alpaca Clang. Writing Alpaca program by hand is a very trick thing and it is very error prone. Reason: a programmer needs to identify the write-after-read dependencies, change variables' names, and modify instructions accordingly, in general writing Alpaca code by hand is not a recommended, for that a compiler is needed}

@@

%\sys is efficient and easy to use across our benchmarks.

@@

Our aim is to assess \sys as detailed as possible. For this we have characterized \sys runtime performance (execution time) considering task adaptation: task coalescing and downscaling. We also characterize \sys overhead showing precisely what is the source of \sys superior performance. Additionally, we characterize \sys code.

@@

We characterize \sys by studying how its performance varies due to task adaptation. We start with evaluating the task coalescing mechanism.

\textbf{Coalescing Strategies.} We first need to assess the performance of all coalescing strategies introduced by us in Section~\ref{sec:task_coalescing}. Figure~\ref{fig:coalescing} shows the run time of \sys's two coalescing strategies normalized to the run time without coalescing. We show data from experiments with intermittent power, where intermittency was generated in software
%\todo{Say briefly how we generate full reset with MSP430}{Amjad}
by triggering a reset from software at intervals that were uniformly distributed with an average power availability and unavailability interval of 15\,ms and 10\,ms respectively. Each application ran with the same generated pattern for the fairness of comparison. The results show the benefit from coalescing for most applications, with the
exception of dft, where wasted work dominated the gains from coalescing.
 %\todo{why coalescing for dft does not work but in Fig. 9 does?}{Amjad}
The difference in performance between HC and TSHC strategies is highly
application-dependent, with some applications benefiting from size awareness
while others suffering, due to decisions based on inaccurate prediction of the
actual task energy consumption. The TSHC gains are particularly small (or negative) for applications with narrower range of task sizes in Figure~\ref{fig:task_profiling}.
%\todo{say why this difference is small}{Amjad}.
%For this reason we shall proceed with HD coalescing strategy in subsequent evaluations.

@@

\begin{table}
	\begin{tabular}{| c | c | c | c | c |}
		\hline
		\multirow{2}{*}{Application} & \multicolumn{2}{ c |}{Memory footprint} & \multirow{2}{*}{No. tasks} & \multirow{2}{*}{SLOC} \\
		\cline{2-3}
		{} & \sys & Alpaca & {} & {} \\
		\hline\hline
				\textbf{ar} & --- & --- & --- & ---\\
		\hline
				\textbf{bc} & --- & --- & --- & ---\\
		\hline
				\textbf{cuckoo} & --- & --- & --- & ---\\
		\hline
				\textbf{dijkstra} & --- & --- & --- & ---\\
		\hline
				\textbf{fft} & --- & --- & --- & ---\\
		\hline
				\textbf{sort} & --- & --- & --- & ---\\
		\hline
	\end{tabular}
		\caption{Comparison between \sys and Alpaca benchmarks.}
		\label{table:compiler_result}\vspace{-0.5cm}
\end{table}
